Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-04-20 Scripts/Initial_Analysis.Rmd
Small changes to the code

@@

  # Get model data from spps
  Spp_Dist <- dbem_import(
    taxon_key = taxon_key,
    year = year,
    data_type = "Catch",
    ensamble = ensamble,
    path = path
  )

@@

@@

@@

@@

      return(Distance_Data)

@@

    Centroids_Data <- bind_rows(
      lapply(Ids,CentroidsFx)
    )

@@

  Centroids_id <- Centroids %>% 
    filter(neighbour_id %in% Ids)

>>>>

This function estimates the distance between the centroid of each neighbouring EEZ and the distribution of the species along both EEZs. We define species centroid as the tile with the highest value of maimum catch potential from all of the species distribution in each year.

@@

  # ----------------- #
  # Get model data from spps for one ensamble
  #  ---------------- #

  Spp_Dist <- dbem_import(
    taxon_key = taxon_key,
    year = year,
    data_type = "Catch",
    ensamble = ensamble,
    path = path
  )

  # ----------------- #
  # Extra step 
  # ----------------- #

  #### Creates a data to control computational time
  if(file.exists("~/Desktop/spp_df.csv") == FALSE){
    spp_df <- tibble() %>% 
      write_csv(.,
                "~/Desktop/spp_df.csv")
  }

@@

  # ----------------- #
  # Estimate distance between centroids
  # ----------------- #

  # Filter only the transboundary nature of the species 
  Trans_Spp <- Spp_Dist %>%
    left_join(index_code,
              by= "index") %>% 
    filter(!is.na(value)) %>% 
    semi_join(Transboundary_spp, # filter only transboundary cases
              by = c("taxon_key","eez_name")
    )

  # ----------------- #
  # Extra step 
  # ----------------- #
  # Controls for cases with no-data
  nr <- nrow(Trans_Spp)
  if(nr > 0){

@@

    # ----------------- #
    # Centroid function
    # ----------------- #

    # This function estimates the distance of each neighbouring EEZ
    # It uses Ids wich is a pre-determine identifier of neighbouring
    # EEZs. Fo example Peru and Chile have Id = 167, and viceversa

@@

      # Filter data by Ids
      EEZ_ids <- Neighbours_combo %>% 
        filter(neighbour_id == Ids)

@@

      # Centroid is defined as the tile with the higest species value
      Centroids <- Sub_Trans_Spp %>% 
        left_join(EEZ_ids, by = "eez_name") %>% 
        group_by(taxon_key,year,ensamble,neighbour_id) %>%  # for whole distribution
        top_n(1,value) %>% 
        distinct(value,year, .keep_all = TRUE) %>%  # removes duplicates when tile is in between EEZs
        left_join(Sub_EEZ_centroid, by = "taxon_key") %>%
        select(eez_name =eez_name.y, everything() ,-eez_name.x) %>% 
        # Estimate distances between spp centroid and EEZ centroid
        mutate(
          distance = geodist(longitude, # eez longitude
                             latitude,  # eez latitude
                             lon,  # species longitude
                             lat, # species latitude
                             units="km")
        ) %>% 
        select(taxon_key,eez_name,neighbour_id,ensamble,year,distance)

      return(Centroids)

@@

    # Determine the ids
    Ids <- unique(Neighbours_combo$neighbour_id)

    # Run function
    Centroids_Data <- bind_rows(
      lapply(Ids,CentroidsFx)
    )

@@

  # Filter data by neighbouring ID
  Centroids_id <- Centroids %>% 
    filter(neighbour_id %in% Ids)
